---
title: "p8105_hw1_sz3214"
author: "Shizhe Zhang"
date: "2024-09-20"
output: github_document
editor_options: 
  chunk_output_type: console
---

# Problem 1

```{r, results='hide'}

data("penguins", package = "palmerpenguins")
summary(penguins)

```

`species`: Penguin species (Adelie, Chinstrap, Gentoo)

`island`: The island in the Palmer Archipelago (Biscoe, Dream, Torgersen)

`bill_length_mm`: Length of the penguin's bill in millimeters

`bill_depth_mm`: Depth of the penguin's bill in millimeters

`flipper_length_mm`: Length of the penguin's flipper in millimeters

`body_mass_g`: Penguin body mass in grams

`sex`: Penguin's sex (male, female)

The dataset contains `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length of the penguins is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm, after accounting for missing data.


```{r, include=F}
library(ggplot2)
```


```{r}

plot <- ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() + 
  labs(x = "Bill Length (mm)", y = "Flipper Length (mm)", color = "Species")

ggsave("penguinscatter.png", plot = plot)

```



# Problem 2

```{r, include=FALSE}
library(tidyverse)
```

creat a data frame

```{r}

numeric = rnorm(10)

logical = numeric > 0

character = sample(letters, 10, replace = TRUE)

factor = factor(sample(c("Low", "Medium", "High"), 10, replace = TRUE))

df = data.frame(numeric, logical, character, factor)

```

Calculate the mean

```{r}
mean(pull(df, numeric))
mean(pull(df, logical))
mean(pull(df, character))
mean(pull(df, factor))
```

Numeric and logical variables works while character and factor don't work.

```{r, results='hide'}
df_numeric = mutate(df, 
    logical_vals = as.numeric(logical),
    character_vals = as.numeric(character),  
    factor_vals = as.numeric(factor)  
  )
```

There is a warning about character variable.
Because converting characters to numeric typically results in NA since there's no inherent numeric mapping for arbitrary text strings.

It can explain why NA happened when took the mean of character variable.



